\newglossaryentry{monoblock}{
	name=Monoblock,
	description={A unit brick made of a tungsten armour with a CuCrZr cooling pipe and a copper interlayer},
}
\newglossaryentry{plasma}{
	name=Plasma,
	description={Ionised gas. Sometimes refered as the fourth state of matter.}
}
\newglossaryentry{divertor}{
	name=Divertor,
	description={Component of a tokamak diverting the magnetic field lines creating one or several X-points. The divertor is responsible for exhausting heat and particle from the plasma. The targets of the divertor is where the plasma is directed to absorb heat and particle fluxes.},
}
\newglossaryentry{strike point}{
	name=Strike point,
	description={Location on the divertor where the serparatrix crosses the solid target. It is where the highest heat and particle fluxes are observed.},
}
\newglossaryentry{fuel recycling}{
	name=Fuel recycling,
	description={Phenomenon occuring when particles from the plasma are neutralised at the walls and ionised again.}
}
\newglossaryentry{breeding blanket}{
	name=Breeding blanket,
	description={Components of a fusion reactor responsible for producing tritium from the neutrons of the fusion reactions.},
}
\newglossaryentry{first wall}{
	name=First wall,
	description={Cover of the inner surface of the vacuum vessel in front of the plasma.},
}

\newglossaryentry{isotope}{
	name=Isotope,
	description={Member of a family of elements sharing the same number of protons but different numbers of neutrons.}
}
\newglossaryentry{transmutation}{
	name=Transmutation,
	description={Conversion of a chemical element into another chemical element by changing the number of neutrons or protons in the nucleus.}
}
\newglossaryentry{transmutation gas}{
	name=Transmutation gas,
	description={Gas produced by transmutation (typically helium or hydrogen).}
}

\newglossaryentry{diffusion}{
	name=Diffusion,
	description={For particles: process resulting from the random motion of particles from high concentration regions to regions of low concentrations. For heat: transport of thermal energy from high temperature regions to low temperature regions.}
}
\newglossaryentry{permeation}{
	name=Permeation,
	description={Transport of particles through a material membrane.}
}
\newglossaryentry{advection}{
	name=Advection,
	description={Transport of particles (or heat) via motion of the medium (as opposed to diffusion where the medium can be immobile).}
}
\newglossaryentry{trapping}{
	name=Trapping,
	description={Process involving a particle being retained in a potential energy well.}
}
\newglossaryentry{detrapping}{
	name=Detrapping,
	description={Opposite to trapping.}
}
\newglossaryentry{Soret effect}{
	name=Soret effect,
	description={Diffusion assisted by thermal gradients.}
}
\newglossaryentry{thermophoresis}{
	name=Thermophoresis,
	description={See Soret effect.}
}


\newglossaryentry{dislocation loop}{
	name=Dislocation loop,
	description={Defects formed by agglomerations of point-defects into planes.}
}
\newglossaryentry{self-interstitial}{
	name=Self-interstitial,
	description={An atom initially in the lattice located at interstitial sites.}
}
\newglossaryentry{vacancy}{
	name=Vacancy,
	description={Defect in the lattice where a metal atom is missing.},
	plural=vacancies
}
\newglossaryentry{Frenkel pair}{
	name=Frenkel pair,
	description={A self-interstitial atom and a vacancy.}
}
\newglossaryentry{trap mutation}{
	name=Trap mutation,
	description={Process where over-pressurised helium clusters eject a metal lattice atom creating a Frenkel pair.}
}
\newglossaryentry{self-trapping}{
	name=Self-trapping,
	description={See trap mutation entry.}
}

\newglossaryentry{loop punching}{
	name=Loop punching,
	description={Helium bubble growth mechanism leading to the formation of a dislocation loop.}
}
\newglossaryentry{fuzz}{
	name=Fuzz,
	description={Porous, nanostructure sometimes observed on tungsten under helium irradiation.}
}
\newglossaryentry{tendril}{
	name=Tendril,
	description={Nanometre-thick columns forming the fuzz.}
}
\newglossaryentry{blistering}{
	name=Blistering,
	description={Formation of blisters: plastic deformation (swelling) of the metal near the surface due to high pressure in bubbles.}
}
\newglossaryentry{bursting}{
	name=Bursting,
	description={Explosion of a gas bubble near the metal surface.}
}


\newglossaryentry{fluence}{
	name=Fluence,
	description={Total quantitiy of particles a sample has been exposed to over a given period of time. Product of the particle flux by the exposure time.}
}
\newglossaryentry{retention}{
	name=Retention,
	description={Local concentration of soluted species (hydrogen or helium) including the mobile species and the trapped ones.}
}
\newglossaryentry{inventory}{
	name=Inventory,
	description={Total quantity of particles in a domain (sample, component, reactor...). It can be obtained by integrating the retention over the domain.}
}
\newglossaryentry{startup inventory}{
	name=Startup inventory,
	description={Tritium inventory required by new reactors to account for the initial tritium losses (processing time, trapping in components...).}
}

% Glossary entries (used in text with e.g. \acrfull{fpsLabel} or \acrshort{fpsLabel})
\newacronym{H}{H}{Hydrogen}
\newacronym{He}{He}{Helium}
\newacronym{D}{D}{Deuterium}
\newacronym{T}{T}{Tritium}
\newacronym{Li}{Li}{Lithium}
\newacronym{W}{W}{Tungsten}


\newacronym[longplural={Plasma Facing Units}, shortplural={PFUs}]{pfuLabel}{PFU}{Plasma Facing Unit}
\newacronym[longplural={Plasma Facing Materials}, shortplural={PFMs}]{pfm}{PFM}{Plasma Facing Material}
\newacronym{cfc}{CFC}{Carbon fiber composite}
\newacronym{ivt}{IVT}{Inner Vertical Target}
\newacronym{ovt}{OVT}{Outer Vertical Target}
\newacronym{isp}{ISP}{Inner Strike Point}
\newacronym{osp}{OSP}{Outer Strike Point}

\newacronym{hcpb}{HCPB}{Helium-Cooled-Pebble-Bed}
\newacronym{wcll}{WCLL}{Water-Cooled-Lithium-Lead}
\newacronym{hcll}{HCLL}{Helium-Cooled-Liquid-Lead}
\newacronym{dcll}{DCLL}{Dual-Coolant-Lithium-Lead}
\newacronym{tbr}{TBR}{Tritium breeding ratio}
\newacronym{fpy}{FPY}{Full power year}


\newglossaryentry{tokamak}{
	name=Tokamak,
	description={Toroidal fusion reactor using magnetic fields to confine the plasma. Acronym for "TOroidalnaïa KAmera s MAgnitnymi Katouchkami", which means "Toroidal chamber with magnetic coils".}
}
\newglossaryentry{stellarator}{
	name=Stellarator,
	description={Toroidal fusion reactor using magnetic fields to confine the plasma. The difference with the tokamak is the twisted magnetic coils and the absence of a central solenoid inducing a current in the plasma.}
}
\newacronym{candu}{CANDU}{CANada Deuterium Uranium reactor}
\newacronym{west}{WEST}{Tungsten Environment Steady state Tokamak}
\newacronym{jet}{JET}{Joint European Torus}
\newacronym{iter}{ITER}{International Thermonuclear Experimental Reactor}
\newacronym{sparc}{SPARC}{Soonest Private-funded Affordable Robust Compact}
\newacronym{arc}{ARC}{Affordable Robust Compact}
\newacronym{nif}{NIF}{National Ignition Facility}
\newacronym{mast-u}{MAST-U}{Mega Amp Spherical Tokamak Ugrade}
\newacronym{step}{STEP}{Spherical Tokamak for Electricity Production}
\newacronym{ukaea}{UKAEA}{United-Kingdom Atomic Energy Authority}

\newacronym{md}{MD}{Molecular Dynamics}
\newacronym{dft}{DFT}{Density Functional Theory}
\newacronym{eels}{EELS}{Electron Energy Loss Spectroscopy}
\newacronym{tds}{TDS}{Themo-Desorption Spectroscopy}

\newacronym{bcc}{bcc}{Body-Centered Cubic (type of metallic lattice)}
\newglossaryentry{lattice}{
	name=Lattice,
	description={Three-dimensional crystalline structure of metals. The lattice is how the atoms are ordered within a metal.}
}

\newacronym{fdm}{FDM}{Finite Difference Method}
\newacronym{fem}{FEM}{Finite Element Method}
\newacronym{festim}{FESTIM}{Finite Element Simulation of Tritium in Materials}
\newacronym{tmap7}{TMAP7}{Tritium Migration Analysis Program, Version 7}
\newacronym{hiipc}{HIIPC}{Hydrogen Isotope Inventory Processes Code}
\newacronym{crds}{CRDS}{Coupled Reaction Diffusion System}
\newacronym{mhims}{MHIMS}{Migration of Hydrogen Isotopes in MaterialS}
\newacronym{tessim}{TESSIM}{Tritium Extraction System SIMulator}
\newacronym{hit}{HIT}{Hydrogen Isotope Transport code}
\newglossaryentry{achlys}{
	name=ACHLYS,
	description={Hydrogen transport code developed by UKAEA}
}
